Species motif participation provides unique information about species risk of extinction

### 2023-04-22 manuscript/reorder_main_text.tex
Updates from Overleaf

>>>>

    \begin{figure}[hb!]
        \centering
        \includegraphics[width=\textwidth]{figures/persistence_omnivory_detailpers.eps}
        \label{omnivory_plus_SC}
        \end{figure}

    \begin{figure}[hb!]
        \centering
        \includegraphics[width=\textwidth]{figures/persistence_chain_detailpers.eps}
        \label{chain_plus_SC}
        \end{figure}

    \begin{figure}[hb!]
        \centering
        \includegraphics[width=\textwidth]{figures/persistence_apparent_detailpers.eps}
        \label{apparent_plus_SC}
        \end{figure}

    \begin{figure}[hb!]
        \centering
        \includegraphics[width=\textwidth]{figures/persistence_direct_detailpers.eps}
        \label{direct_plus_SC}
        \end{figure}
